Constant-round Blind Classical Verification of Quantum Sampling

### 2020-04-09 qpip0.tex

\begin{lemma}\label{lem:urmila-binding}[binding property of  Protocol~\ref{proto:urmila4}\cite{FOCS:Mahadev18a}]
If a prover's strategy\hannote{need clarification} result in passing the testing round with probability $1-\negl(n)$, then there must exist a $\rho$ such that for all $h$, the prover will produce a $z$ on the Hadamard round that is $\negl(n)$-Q-computationally indistinguishable from $M_{XZ}(\rho,h)$\hannote{add notation}, unless LWE can be efficiently solved by a quantum computer. 
\end{lemma}

\begin{rmk}
Note that even a honest prover has complete freedom in choosing $\rho$, so protocol~\ref{proto:urmila4} didn't make the prover commit to a particular state. What it actually does is let the prover commit to a particular $XZ$ measurement on $\rho$. This is good enough for our application, since we will feed the $XZ$ measurement results into the verification of $\QPIP_1$ protocol to ensure that the prover pick the history state as $\rho$.
\end{rmk}

>>>>

\begin{lemma}\label{lem:urmila-binding}[binding property of  Protocol~\ref{proto:urmila4}\cite{FOCS:Mahadev18a}]
If a prover's strategy in Protocol~\ref{proto:urmila4}\hannote{need clarification} results in passing the testing round with probability $1-\negl(n)$, then there must exist a $\rho$ such that for all $h$, the prover will produce a $z$ on the Hadamard round that is $\negl(n)$-Q-computationally indistinguishable from $M_{XZ}(\rho,h)$\hannote{add notation}, unless LWE can be efficiently solved by a quantum computer. 
\end{lemma}

Note that even a honest prover has complete freedom in choosing $\rho$, so protocol~\ref{proto:urmila4} didn't make the prover commit to a particular state. What it actually does is let the prover commit to a particular $XZ$ measurement on $\rho$. This is good enough for our application, since we will feed the $XZ$ measurement results into the verification of $\QPIP_1$ protocol to ensure that the prover pick the history state as $\rho$ as we will show next.

We combine the commitment Protocol, Protocol~\ref{proto:urmila4}, and the $\QPIP_1$ Protocol, Protocol~\ref{ProtoQPIP1}, to get a naive $\QPIP_0$ Protocol for $\SampBQP$ that has no soundness guarantee.

\begin{protocol}{naive $\QPIP_0$ protocol  for the $\SampBQP$ instance $(D_x)_{x\in\set{0, 1}^*}$}
	\label{proto:qpip0_naive}

	Inputs: \Ethan{Should the $\SampBQP$ instance be an input?}
	\begin{itemize}
		\item Classical input $x\in\zo^n$ to the $\SampBQP$ instance
		\item Error parameter $\varepsilon\in(0, 1)$
	\end{itemize}

 	Ingrediants:
 	\begin{itemize}
 		\item Let $C$ be a quantum circuit consisting of only Hadamard and Toffoli gates, which on input $x$ samples from some $C_x$ such that $\norm{C_x-D_x}\leq\varepsilon$.
 		\item Let $C'$ be $C$ padded with $\frac{T}{\varepsilon}$ identity gates at the end.
 		\item Let $H_{C'(x)}$ be the local Hamiltonian instance associated with the computation of $C'(x)$.
		\item Let $\ket{\psi_{C'(x)}}$ be the ground state of $H_{C'(x)}$.
%  		\item Let $\cVGS$ be the way to verify said ground state as defined in \Cref{AlgGroundStateCheck}. \Ethan{TODO wording needs fix...? How?}
 	\end{itemize}

	Protocol:
	\begin{enumerate}
	\item The verifier choose a $XZ$-measurement $h$ over  $M=\frac{T^{21}}{\varepsilon^{33}}$  copies of $\ket{\psi_{C'(x)}}$ from the distribution emergent from by Step~\ref{step:qpip1-verify} of Protocol~\ref{ProtoQPIP1}.

	\item The verifier and prover run Protocol~\ref{proto:urmila4}, with the following parameters: $h$ is chosen from previous step, $n_{commit}=M \times$ (number of qubits in $\ket{\psi_{C'(x)}}$), where $n_{commit}$ is the $n$ for Protocol~\ref{proto:urmila4}, and the honest prover choose $M$ copies of $\ket{\psi_{C'(x)}}$ as $\rho$.

	\item If $c=1$, the verifier finished the verification step of Protocol~\ref{ProtoQPIP1} by using $z$ from Protocol~\ref{proto:urmila4} as the measurement result he would get and outputs $(d,z_{naive})$

	\end{enumerate}
\end{protocol}

\begin{lemma}\label{lem:naive-qpip0-binding}[binding property of  Protocol~\ref{proto:qpip0_naive} ]
If a prover's strategy in Protocol~\ref{proto:qpip0_naive} results in passing the testing round with probability $1-\negl(n)$, then conditioning on the Hadamard round being chosen, $\norm{(d,z_{naive})-(d,z_{ideal})}_q \leq O(\eps)$.

, unless LWE can be efficiently solved by a quantum computer. 
\end{lemma}
